My title

### 2024-11-26 paper/paper.qmd
introduction and abstract added

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: [https://github.com/iJustinn/Canadian_Grocery_Analysis.git](https://github.com/iJustinn/Canadian_Grocery_Analysis.git)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: [https://github.com/iJustinn/Canadian_Grocery_Analysis.git](https://github.com/iJustinn/Canadian_Grocery_Analysis.git)."
date: today
date-format: long
abstract: "This study analyzes beef pricing dynamics in the Canadian retail market, focusing on two vendors: Walmart and T&T. Using Bayesian linear regression, we found that historical pricing and vendor-specific strategies significantly influence current beef prices, with Walmart displaying more price stability and T&T showing greater variability. These findings reveal how both market-wide and vendor-specific factors shape beef pricing, offering insights that could help retailers refine their pricing strategies and support policymakers in addressing food affordability. This paper provides a clearer understanding of the interplay between cultural preferences and retail strategies in determining food prices."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The pricing of grocery products, particularly beef, plays a significant role in understanding consumer behavior and market dynamics within the Canadian retail sector. Beef, as a staple of many households, exhibits complex pricing behaviors influenced by a variety of factors, including vendor strategies, historical pricing, and seasonal trends. The broader context for this study lies in exploring how large-scale retailers and specialty stores adjust their beef prices over time and how these changes reflect broader economic and cultural trends. Given the increasing concerns around food affordability and accessibility, understanding the dynamics of beef pricing is not only crucial for consumers but also for stakeholders involved in food distribution and policy-making.

This paper specifically focuses on two prominent vendors, Walmart and T&T, to examine how beef pricing varies across different types of retail environments. Walmart, as a major multinational retailer, represents mainstream, standardized pricing strategies, while T&T, catering primarily to Asian communities, represents a more specialized market segment. By analyzing data from these two vendors, this paper aims to address an important gap in understanding how cultural preferences and retail strategies influence product pricing. While previous studies have highlighted general trends in food pricing, they often overlook the nuanced differences between general retail chains and culturally specific stores. This paper fills that gap by providing an in-depth analysis of beef pricing patterns across these two distinct retail settings.

Using a Bayesian linear regression approach, this study examines the effect of historical pricing, vendor-specific strategies, and seasonal factors on current beef prices. The analysis finds that old prices significantly predict current pricing, indicating a high degree of price consistency. Additionally, notable differences in pricing strategies between Walmart and T&T suggest that these vendors approach their markets with distinct pricing objectives, with Walmart favoring price stability and T&T showing more variability in pricing, possibly to cater to niche preferences. The findings are significant as they reveal the underlying mechanisms of price determination in a diverse retail environment, highlighting both market-wide factors and vendor-specific influences. Such insights could be useful for retailers looking to optimize their pricing strategies and for policymakers interested in addressing food affordability concerns.

The structure of the paper is organized as follows: @sec-data outlines the data collection and cleaning process, along with a description of the outcome and predictor variables used in the analysis. @sec-model introduces the forecasting models and discusses the rationale behind choosing these models for beef pricing prediction. @sec-result then presents the main findings, including a breakdown of vendor-level pricing effects and seasonal trends. Finally, @sec-discussion interprets the results, highlighting significant trends, comparing vendor strategies, and discussing potential limitations of the analysis.
